---
title: "Lab01"
author: "Elijah Boulton"
date: "January 20, 2019"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Task 1

The working directory

```{r}
getwd()
```

# Task 2

First 6 lines of data

```{r}
ddt = read.csv("DDT.csv")
head(ddt)
```

# Task 3

Qualitative variables are listed as true, quantitative are listed as false:

```{r}
unlist(lapply(ddt, is.factor))
```

Species in the data set:

```{r}
levels(ddt$SPECIES)
```

Data for LMBASS with a weight greater than 800 grams

```{r}
temp = with(ddt, ddt[WEIGHT>800 & SPECIES == "LMBASS",])
print(temp)
```

Data for fish from the SCM river with DDT greater than 4.0

```{r}
temp = with(ddt, ddt[RIVER == "SCM" & DDT > 4.0,])
print(temp)
```

Clicker Questions:

Q.1   The mean length of fish in ddt is 42.81

Q.2   The standard deviation of fish weight in ddt is 376.5461

Q.3   The answer is 0

Q.4   The last value of v/20 is 1.00


# Task 4

Table of the rivers

```{r}
tabRVR = table(ddt$RIVER)
print(tabRVR)
```

Colored barplot of the rivers

```{r}
barRVR = barplot(tabRVR, beside = TRUE, col = 1:4, legend.text = TRUE, main = "Number of Fish per River")
```

Table of rivers crossed with species of fish

```{r}
tabRF = with(ddt, table(SPECIES, RIVER))
print(tabRF)
```

Barplot of river crossed with species of fish

```{r}
barRF = barplot(tabRF, main = "Species of Fish in Each River", legend.text = TRUE, width = 3, xlim = c(0, 20))
```

# Task 5

Pie chart of fish species

```{r}
tabS = with(ddt, table(SPECIES))
pie(tabS, main = "Fish of Each Species")
```

Pie chart of rivers

```{r}
tabR = with(ddt, table(RIVER))
pie(tabR, main = "Fish in Each River")
```

# Task 6

Boxplot of DDT levels

```{r}
BoxDDT = boxplot(ddt$DDT, main = "DDT Levels in Fish")
```

Boxplot of fish weight

```{r}
BoxW = boxplot(ddt$WEIGHT, main = "Fish Weight")
```

Boxplot of fish length

```{r}
BoxL = boxplot(ddt$LENGTH, main = "Fish Length")
```

# Task 7

Coplot of length vs weight for each river

```{r}
LWRcoplot = coplot(LENGTH~WEIGHT|RIVER, data = ddt)
```

Coplot of DDT vs weight for each species

```{r}
LWRcoplot = coplot(DDT~WEIGHT|SPECIES, data = ddt)
```

# Task 8








